\documentclass{article}
\input{/home/darin/MEGA/isye/preamble-homework.tex}

\includecomment{solution}
%\excludecomment{solution}  % comment this out to create the solutions

\begin{document}
\subsection{Cooperation}

This exercise serves as an introduction to NetLogo. In this simulated
model there are two types of cows, greedy and cooperative.  We want to
investigate the circumstances under which being greedy (or being
cooperative) is more beneficial to the respective populations. \emph{Brief}
answers to the questions are fine; a sentence or two will suffice.


\begin{enumerate}
\item Download and install the Netlogo software from\\
  \url{http://ccl.northwestern.edu/netlogo/index.shtml}.
\item Open the Models Library. In the Social Science folder, open the ``Cooperation''
  model.
\item On the ``Info'' tab, read about the model.

\item Run the model with the default settings. Which population ``wins''
  when the model reaches steady--state?
\item Our goal is to find settings for which it is better to be
  a member of the cooperative population. Let's experiment with
  two controls, stride--length and metabolism.
  \begin{enumerate}
  \item Slowly decrease stride--length. What is the result for each population?
    Make sure you run the model long enough to observe steady--state behavior.
  \item Set stride--length back to it's default value of 0.8. Now slowly increase
    metabolism. What is the result?
  \end{enumerate}
\item In general, do the results intuitively make sense? Are there any lessons
  that can be applied to humans and the planet?
  \end{enumerate}

  \emph{Note:} This is an evolutionary biology model. In the
  Prisoner's Dilemma model (later) we will investigate the
  consequences of individual decisions to be greedy (to act in one's
  own self interest) or to cooperate.

\end{document}
